Generative Adversarial Networks

### 2017-12-09 cs6735/assignment/report.tex
add ece labs

\section{Results}
\begin{table}
  \begin{tabular}{ |c|c|c|c|c|c| }
    \hline
    Algorithm               Breast Cancer   & Car      & Letter   & E. Coli  & Mushroom \\ \hline
    ID3                     & 97.994\%      & 90.634\% & 81.909\% & 100.00\% & 99.998\% \\ \hline
    Naïve Bayes             & 97.663\%      & 81.940\% & 79.455\% & 100.00\% & 95.952\% \\ \hline
    AdaBoost on ID3         & 98.715\%      & 88.822\% & 83.389\% & 100.00\% & 99.446\% \\ \hline
    AdaBoost on Naïve Bayes & 98.626\%      & 91.367\% & 77.725\% & 100.00\% & 99.744\% \\ \hline
    Random Forest           & 97.592\%      & 91.175\% & 84.316\% & 100.00\% & 99.865\% \\ \hline
    K-Nearest Neighbor      & 98.050\%      & 89.763\% & 87.886\% & 100.00\% & 99.826\% \\ \hline
  \end{tabular}
  \caption{Results of the six implemented algorithms on five UCI Machine Learning repositories. Accuracy calculated using 10 times 5-fold cross validation.}
\end{table}

\begin{table}
  \begin{tabular}{ |c|c|c|c|c|c| }
    \hline
    Algorithm               & Breast Cancer & Car      & Letter   & E. Coli  & Mushroom \\ \hline
    ID3                     & 1.465\%       & 4.061\%  & 8.981\%  & 100.00\% & 0.017\%  \\ \hline
    Naïve Bayes             & 1.678\%       & 3.373\%  & 10.388\% & 100.00\% & 2.128\%  \\ \hline
    AdaBoost on ID3         & 1.216\%       & 3.085\%  & 6.678\%  & 100.00\% & 1.081\%  \\ \hline
    AdaBoost on Naïve Bayes & 1.394\%       & 1.987\%  & 9.275\%  & 100.00\% & 0.652\%  \\ \hline
    Random Forest           & 1.597\%       & 5.171\%  & 9.711\%  & 100.00\% & 0.702\%  \\ \hline
    K-Nearest Neighbor      & 1.118\%       & 3.967\%  & 7.001\%  & 100.00\% & 0.433\%  \\ \hline
  \end{tabular}
  \caption{Results of the six implemented algorithms on five UCI Machine Learning repositories. Accuracy calculated using 10 times 5-fold cross validation.}
\end{table}

>>>>

\section{Results}
\begin{table}
  \begin{tabular}{ |c|c|c|c|c|c| }
    \hline
    Algorithm               Breast Cancer   & Car      & Letter   & E. Coli  & Mushroom \\ \hline
    ID3                     & 97.994\%      & 90.634\% & 81.909\% & 88.234\% & 99.998\% \\ \hline
    Naïve Bayes             & 97.663\%      & 81.940\% & 79.455\% & 65.048\% & 95.952\% \\ \hline
    AdaBoost on ID3         & 98.715\%      & 88.822\% & 83.389\% & 100.00\% & 99.446\% \\ \hline
    AdaBoost on Naïve Bayes & 98.626\%      & 91.367\% & 77.725\% & 100.00\% & 99.744\% \\ \hline
    Random Forest           & 97.592\%      & 91.175\% & 84.316\% & 100.00\% & 99.865\% \\ \hline
    K-Nearest Neighbor      & 98.050\%      & 89.763\% & 87.886\% & 100.00\% & 99.826\% \\ \hline
  \end{tabular}
  \caption{Results of the six implemented algorithms on five UCI Machine Learning repositories. Accuracy calculated using 10 times 5-fold cross validation.}
\end{table}

\begin{table}
  \begin{tabular}{ |c|c|c|c|c|c| }
    \hline
    Algorithm               & Breast Cancer & Car      & Letter   & E. Coli  & Mushroom \\ \hline
    ID3                     & 1.465\%       & 4.061\%  & 8.981\%  & 3.492\% & 0.017\%  \\ \hline
    Naïve Bayes             & 1.678\%       & 3.373\%  & 10.388\% & 1.328\% & 2.128\%  \\ \hline
    AdaBoost on ID3         & 1.216\%       & 3.085\%  & 6.678\%  & 100.00\% & 1.081\%  \\ \hline
    AdaBoost on Naïve Bayes & 1.394\%       & 1.987\%  & 9.275\%  & 100.00\% & 0.652\%  \\ \hline
    Random Forest           & 1.597\%       & 5.171\%  & 9.711\%  & 100.00\% & 0.702\%  \\ \hline
    K-Nearest Neighbor      & 1.118\%       & 3.967\%  & 7.001\%  & 100.00\% & 0.433\%  \\ \hline
  \end{tabular}
  \caption{Results of the six implemented algorithms on five UCI Machine Learning repositories. Accuracy calculated using 10 times 5-fold cross validation.}
\end{table}
